Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-29 paper/main.tex
update labels

% --------------------------------------------------------------------------------------------------
\subsubsection{With Division}

@@

By using \texttt{cellular\_raza}, we can make use of multiple threads for running a single numerical
simulation, using the built-in parallelization methods (see Supplementary Material,
Figure~\ref{fig:performance}).

>>>>

% --------------------------------------------------------------------------------------------------
\subsubsection{With Division}
\label{sec:application-1-with-division}

@@

By using \texttt{cellular\_raza}, we can make use of multiple threads for running a single numerical
simulation, using the built-in parallelization methods (see Supplementary Material,
Figure~\ref{fig:timings-crm_divide}).
